Perihelion advance of Mercury

### 2019-06-17 perihelion_advance_of_mercury.Rmd
more work

The orbit of Mercury has long been known to advance at a rate of about 6400'' [seconds of arc] per century.  Various classical phenomena, such as the effects of Venus, and the oblateness of the sun, account for all but 43 seconds of arc and this remaining amount puzzled astronomers for many years. According to Einstien and others, the general theory of relativity predicts an additional precession of almost exactly 43 seconds per century.  In this document I will calculate the precessional rate using numerical methods.

@@

closely agreeing with Einstein's original prediction of 43.  A more careful analysis would account for the nonzero mass of Mercury.

>>>>

The orbit of Mercury has long been known to advance at a rate of about
575'' [seconds of arc] per century.  Various classical phenomena, such
as the effects of Venus, and the oblateness of the sun, account for
all but 43'' and this remaining amount puzzled astronomers for many
years.  According to Einstien and others, the general theory of
relativity predicts an additional precession of almost exactly 43
seconds per century, thus closing the gap between expectation and
observation.  In this document I will calculate the precessional rate
using numerical methods.

@@

closely agreeing with Einstein's original prediction of 43''.  A more
careful analysis would account for the nonzero mass of Mercury.
